Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-08 Manuscript.Rmd
The thresholding works, but doesn't really change the matrix-visualizations

@@

With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 total TRs from four scanning sessions over two days). Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nrow(Summaries[[1]])` total vertices). After correcting for multiple testing, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas. On average, networks had high densities (i.e. highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`). This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].

@@

# Store thre FV thresholds for all subject 
threshDF <- data_frame(SubjID = substring(subjList,1,6),
                       Lower = NA,
                       Upper = NA)
for (i in seq_along(tempList)) {
  if (is.null(tempList[[i]]$result)) {
    threshDF[i,2:3] <- c(0,0)
  } else {
    threshDF[i,2] <- tempList[[i]]$result[1]
    threshDF[i,3] <- tempList[[i]]$result[2]
  }
}
```
### *Pattern stability over time*

@@

### *Partition Comparison: Day 1 vs Day 2*

@@

@@

@@

``` {r Partition comparison: session similarity matrices (Fig. 7), fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess_plot, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

>>>>

# Whether to apply subject-wise thresholds on maps or not
threshMaps <- TRUE

@@

*NOTE: It might be better to just avoid cluster comparisons at this pre-threshold level*
With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 total TRs from four scanning sessions over two days). Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nrow(Summaries[[1]])` total vertices). After correcting for multiple testing, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas. On average, networks had high densities (i.e. highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`). This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].

@@

### *Pattern stability over time*

@@

# Store thre FV thresholds for all subject 
threshDF <- data_frame(SubjID = substring(subjList,1,6),
                       Lower = NA,
                       Upper = NA)
for (i in seq_along(tempList)) {
  if (is.null(tempList[[i]]$result)) {
    threshDF[i,2:3] <- c(0,0)
  } else {
    threshDF[i,2] <- as.numeric(tempList[[i]]$result[1])
    threshDF[i,3] <- as.numeric(tempList[[i]]$result[2])
  }
}

### *Partition Comparison:Thresholded Full Datasets*
``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
# Apply threshold to Summaries
if (threshMaps) {
  for (i in seq(nSubj)) {
  Summaries[[i]] <- Summaries[[i]] %>%
    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
    mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
  }
}

```
### *Partition Comparison: Day 1 vs Day 2*

@@

# Apply threshold to Summaries
if (threshMaps) {
  # create a vector of repeated indices, so each threshold is applied to each subject twice
  threshindex <- rep(seq(nSubj), each = 2)
  count <- 1
  for (i in threshindex) {
    Summaries_halves[[count]] <- Summaries_halves[[count]] %>%
            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
            mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
    count <- count + 1
  }
}

@@

# Apply threshold to Summaries
if (threshMaps) {
  # create a vector of repeated indices, so each threshold is applied to each subject twice
  threshindex <- rep(seq(nSubj), each = 4)
  count <- 1
  for (i in threshindex) {
    Summaries_sess[[count]] <- Summaries_sess[[count]] %>%
            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
            mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
    count <- count + 1
  }
}

@@

``` {r Partition comparison: session similarity matrices (Fig. 7), fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess_plot, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```
